lfl: Linguistic Fuzzy Logic in \R{}

### 2021-01-20 chunks/chunk-fcut.logfact.tex
Adjusted width of R code and output

\begin{Schunk}
% --begin: "fcut.logfact"
\begin{Sinput}
R> logvec <- c(TRUE, FALSE, FALSE, TRUE, TRUE)
R> position <- factor(c("worker", "manager", "worker", "worker", "accountant"))
R> fcut(data.frame(employed = logvec, position = position))
\end{Sinput}
\begin{Soutput}
     employed not.employed position=accountant position=manager position=worker
[1,]        1            0                   0                0               1
[2,]        0            1                   0                1               0
[3,]        0            1                   0                0               1
[4,]        1            0                   0                0               1
[5,]        1            0                   1                0               0
\end{Soutput}
%
% --end: "fcut.logfact"
\end{Schunk}

>>>>

\begin{Schunk}
% --begin: "fcut.logfact"
\begin{Sinput}
R> logvec <- c(TRUE, FALSE, FALSE, TRUE, TRUE)
R> position <- factor(c("worker", "manager", "worker", "worker", "accountant"))
R> fcut(data.frame(employed = logvec, position = position))
\end{Sinput}
\begin{Soutput}
     employed not.employed position=accountant position=manager
[1,]        1            0                   0                0
[2,]        0            1                   0                1
[3,]        0            1                   0                0
[4,]        1            0                   0                0
[5,]        1            0                   1                0
     position=worker
[1,]               1
[2,]               0
[3,]               1
[4,]               1
[5,]               0
\end{Soutput}
%
% --end: "fcut.logfact"
\end{Schunk}
